\documentclass[12pt]{article}
\usepackage{amsmath}

\title{\textbf{Assignment 2}}
\author{ADITYA INGLE\\MIS: 112103050}
\date{\today}

\begin{document}
\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{roman}
\vspace{10mm}
\begin{center}
\huge \bf {COEP Technological University} 
\linebreak \small{(COEP Tech)}\\
\vspace{6mm}
\large \textbf{End Semester Examination} \\  Ordinary Differential Equation And Multivariate Calculus
\\ (MA-16001)
\end{center}
\par\noindent\rule{\textwidth}{1pt}
\\
\vspace{5mm}
\noindent \textbf{Date :} \today \hfill \textbf {Duration :} 1 hour
\\ \textbf {Branches :} All \hfill  \textbf {Max marks} : 60
\\ \textbf {Programme :} S.Y B.Tech \hfill \textbf {Semester :} I
\linebreak
\\ \textbf {Name:}  \hfill \textbf{MIS.NO : }
\linebreak
\\ \textbf{Instructions:}
\linebreak
\\ \textbf{1.} All questions are compulsory.
\\ \textbf{2.} All symbols have their usual meanings.
\\ \textbf{3.} Figures to right indicate course outcomes and full marks.
\\ \textbf{4.} Mobile phones and programmable calculators are not allowed.
\\ \textbf{5.} Writing anything on question paper , exchange of stationary, calculator is strictly not allowed.
\\ \textbf{6.} Write all subparts of question of question together.
\newpage

%Maths Paper:
\section{Maths Paper}
\vspace{5mm}
\subsection{SECTION - A}
\vspace{2mm}
1) Which of the following sequences converge and which diverge? Find the limit of each convergent sequence and justify your answers.\\

(a) $a_n = (-1)^n(1 - \dfrac{1}{n})$ \hspace{15mm} (b) $a_n = \dfrac{\ln n}{n^{\frac{1}{n}}}$\\\\

\noindent
2) For any $\triangle ABC$, prove that -\\
$$a \sin (B-C) + b \sin (C - A) + c \sin (A-B) = 0$$\\

\noindent
3) Find the value of $$\sqrt{3} \csc (20^{\circ}) - \sec (20^{\circ})$$.\\

\noindent
4) Find the value of $f(x) = \dfrac{tan(3x) \ln (x+1)}{\sqrt[3]{\sin^6 x}}$ when x tends to 0.\\\\

\noindent
5) Find $\dfrac{dy}{dx}$ for $ y = e^{6 \log_e (x-1)}$, $ x > 1$.\\\\

\subsection{SECTION - B}
\vspace{2mm}
6) Find the determinant of 
$\begin{bmatrix}
3 & 5 \\ 2 & 4
\end{bmatrix}$.\\\\

\noindent
7) Find $\det (AB)$ if  $A = \begin{bmatrix}
\sin x & \cos x \\ \cos x & -\sin x
\end{bmatrix}$  and  $B = \begin{bmatrix}
2 & \tan x \\ \cos x & 0
\end{bmatrix}$.

\newpage

\subsection{SECTION - C}
\vspace{2mm}
8) Solve the following equations simultaneously:
\begin{align}
2x - 5 y + 3z = 6\\
x - y + 7z = 0\\
3y = 2
\end{align}\\

\noindent
9) Find the value of following definite integrals:\\

(a) \( \int_{0}^{1} \sin x \, dx \) \hspace{15mm} (b) \( \int_{0}^{1} \frac{\ln x}{x} \, dx \)\\\\

\noindent
10) Let k be a number. Then the matrix $A = \begin{bmatrix}
k & 0 & \cdots & 0\\
0 & k & \cdots & 0\\
\vdots & \vdots & \ddots & \vdots\\
0 & 0 & 0 & k
\end{bmatrix}$ is called as ?\\

\indent(A) Triangular Matrix\\
\indent(B) Idempotent Matrix\\
\indent(C) Scalar Matrix\\
\indent(D) None of the Above

\subsection{SECTION - D}
11) Solve the equation $x^2 + 6x + 8$.\\

\noindent
12) Solve the following equations:\\\\
{a) $x^2 + 2x + 3 = 0$\\
b) $x^3 - 7x + 3 = 15$\\
c) $x^5 + 2x + 1 = 0$}


\end{document}